Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-16 paper/v2.0/sections/4_inverse_scattering_time.tex
Add new version of the paper

The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
However, this theory has not been applied for a dressed quantum Hall system in the previous studies. In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq_12}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
\begin{equation} \label{eq_13}
  \begin{aligned}
    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
    & =
    \frac { \varrho^2}{eB}
    \delta(\varepsilon - \varepsilon_{N}) \\
    & \quad\times
    \int_{-\infty}^{\infty} d k_1 \Bigg[
    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
    & \quad\times
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg],
  \end{aligned}
\end{equation}
where $\varrho = \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
A more detailed derivation is given in Appendix \ref{appendix_c}.
We modeled the effect caused by impurities in the considered system as a single perturbation potential.
Since random impurities in a disordered metal offers a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
Thus, the total scattering potential in the 2DEG has been represented as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
Moreover in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.

Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
Since the disorder in the system can not singificantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix. Subsequenty we consider only the central (${l=l'=0}$) diagonal element of the inverse scattering time matrix which has the largest contribution to the transport characteristics. Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
\begin{equation} \label{eq_14}
 \Gamma^{00}_{N}(\varepsilon,k_x) = \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
\end{equation}
which simplifies to
\begin{equation} \label{eq_15}
 \begin{aligned}
   &\Gamma^{00}_{N} (\varepsilon,k_x) \\
   & =
   \frac { \varrho^2}{eB}
   \delta(\varepsilon - \varepsilon_{N}) \\
   & \quad\times
   \int_{-\infty}^{\infty} d k_1 \Bigg[
   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
   \\
   & \quad\times
   \qty|
   \int_{-\infty}^{\infty} dk_2 \;
   {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg].
 \end{aligned}
\end{equation}

\begin{figure}[t]
\includegraphics[scale=0.68]{figures/fig_3}
\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

\begin{figure}[b]
\includegraphics[scale=0.68]{figures/fig_4}
\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

In addition, for a scattering scenario taking place wihtin the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
\begin{equation} \label{eq_16}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)}.
\end{equation}
Then we write the central element of inverse scattering time matrix in the more compact form
\begin{equation} \label{eq_17}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,& k_x) =
    \varrho
    \bigg[
    \int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
    \bigg]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
\begin{equation} \label{eq_18}
    \Lambda_N(k_x) =
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
which can be evaluated with
\begin{widetext}
\begin{equation} \label{eq_19}
    \Lambda_N (k_x) =
    \qty[
    \frac
    {\int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    {\int_{-\infty}^{\infty} d {k}_1 \;
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    ]^{1/2}.
\end{equation}
\end{widetext}

Normalized energy band broadening against x-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
In that study, the authors have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20}. In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
Here, we observe that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field. When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
To analyze these adjustments in detail, we derive a analytical expression for the conductivity of a dressed quantum Hall system in the next section.

>>>>

The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
However, this theory has not been applied for a dressed quantum Hall system in the previous studies. In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq_12}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
\begin{equation} \label{eq_13}
  \begin{aligned}
    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
    & =
    \frac { \varrho^2}{eB}
    \delta(\varepsilon - \varepsilon_{N}) \\
    & \quad\times
    \int_{-\infty}^{\infty} d k_1 \Bigg[
    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
    & \quad\times
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg],
  \end{aligned}
\end{equation}
where $\varrho = \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
A more detailed derivation is given in Appendix \ref{appendix_c}.
We modeled the effect caused by impurities in the considered system as a single perturbation potential.
Since random impurities in a disordered metal offers a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
Thus, the total scattering potential in the 2DEG has been represented as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.

Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
Since the disorder in the system can not significantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix. Subsequently we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics. Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
\begin{equation} \label{eq_14}
 \Gamma^{00}_{N}(\varepsilon,k_x) = \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
\end{equation}
which simplifies to
\begin{equation} \label{eq_15}
 \begin{aligned}
   &\Gamma^{00}_{N} (\varepsilon,k_x) \\
   & =
   \frac { \varrho^2}{eB}
   \delta(\varepsilon - \varepsilon_{N}) \\
   & \quad\times
   \int_{-\infty}^{\infty} d k_1 \Bigg[
   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
   \\
   & \quad\times
   \qty|
   \int_{-\infty}^{\infty} dk_2 \;
   {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg].
 \end{aligned}
\end{equation}

\begin{figure}[t]
\includegraphics[scale=0.68]{figures/fig_3}
\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a  frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

\begin{figure}[b]
\includegraphics[scale=0.68]{figures/fig_4}
\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
\begin{equation} \label{eq_16}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)}.
\end{equation}
Then we write the central element of inverse scattering time matrix in the more compact form
\begin{equation} \label{eq_17}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,& k_x) =
    \varrho
    \bigg[
    \int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
    \bigg]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
\begin{equation} \label{eq_18}
    \Lambda_N(k_x) =
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
which can be evaluated with
\begin{widetext}
\begin{equation} \label{eq_19}
    \Lambda_N (k_x) =
    \qty[
    \frac
    {\int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    {\int_{-\infty}^{\infty} d {k}_1 \;
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    ]^{1/2}.
\end{equation}
\end{widetext}

Normalized energy band broadening against x-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}. In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$. Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
Here, we observe that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field. When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.

### 2021-08-16 paper/v2.0/sections/5_floquet_drude_conductivity.tex
Add new version of the paper

A general theory for the conductivity of a dressed system with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} =&
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are the $x$-directional electric current operator matrix elements' $0$-th Fourier component and the white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2}.
\end{equation}
Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr[\cdot]$ is the trace of the considering operator.

Next, we restrict our analysis into off-resonant regime $\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system. Thus, the $x$-directional longitudinal conductivity given in

@@

where $k_B$ is theBoltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system. Considering the above distribution for extremely low temperature conditions, we can use the following approximation

@@

Following the same steps as above derivation, we can derive the longitudinal conductivity in $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}

>>>>

A general theory for the conductivity of a dressed system with the disorder was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} =&
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are the $x$-directional electric current operator matrix elements' $0$-th Fourier component and the white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2}.
\end{equation}
Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr[\cdot]$ is the trace of the considering operator.

Next, we restrict our analysis into the off-resonant regime $\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system. Thus, the $x$-directional longitudinal conductivity given in

@@

where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system. Considering the above distribution for extremely low-temperature conditions, we can use the following approximation

@@

Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}

### 2021-08-16 paper/v2.0/sections/7_conclusions.tex
Add new version of the paper

In this paper, we introduced a generalized mathematical model for prediciting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light. Under the uniform magnetic field, the charged particles can only settle in discrete energy values which leads to the Landau quantization. We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method. We assumed the impurities in the material as a Gaussian random scattering potential. Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.

Our derived analytical expressions disclosed that the transport characteristics of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
We found that the graphical illustrations that we obtained from these numerical calculatiuons are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
Furthermore, we identified that by increasing the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed. Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems. However, our generalized analysis on conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.

In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties of dressed quantum Hall systems. Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adopted to extend the models that were used to describe the transport characteristics in quantum Hall systems. Owing the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices. As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D opto-electronic nano transistors, enhancing their performance, and inventing novel appliances.

>>>>

In this paper, we introduced a generalized mathematical model for predicting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high-intensity light. Under the uniform magnetic field, the charged particles can only settle in discrete energy values, which leads to the Landau quantization. We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method. We assumed the impurities in the material as a Gaussian random scattering potential. Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.

Our derived analytical expressions disclosed that the transport characteristics of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
Furthermore, we identified that by increasing the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed. Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems. However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.

In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties of dressed quantum Hall systems. Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adapted to extend the models that were used to describe the transport characteristics in quantum Hall systems. Owing to the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices, which are employed as the building blocks of next-generation nanoelectronic devices. As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D optoelectronic nano transistors, enhancing their performance and inventing novel appliances.
